\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Update on Overleaf.
Proof-reading of Rachid's changes

We focus on a specific class of interactions: human-robot collaborative task achievement \cite{alami2013human} 
supported by multi-modal and situated communication. Figure~\ref{fig:hri-dec}
illustrates this context: the human and the robot share a common space and exchange
information through multiple modalities (we specifically consider verbal
communication, deictic gestures and social gaze), and the robot is expected to achieve
interactive object manipulation, fetch and carry tasks and other similar
chores by taking into account, at every stage, the intentions, beliefs,
perspectives, skills of its human partner.  Namely, the robot must be able to
recognise, understand and participate in communication situations, both explicit
(\eg the human addresses verbally the robot) and implicit (\eg the human points
to an object); the robot must be able to take part in joint actions, both
pro-actively (by planning and proposing resulting plans to the human) and
reactively; the robot must be able to move and act in a safe, efficient and
legible way, taking into account social rules like proxemics.

@@

This translates into several decisional, planning, representation skills that
need to be available to the robot \cite{alami2011robot}. It must be able \item to represent and manipulate symbolic belief states, \item to acquire and keep them up-to-date with respect to the state of the world and the task at hand, \item to build and
iteratively refine shared (human-robot) plans, \item to instantiate and execute
the actions it has to perform, and conversely, to monitor those achieved by
its human partner.

@@

Importantly, this architecture is fully implemented and we demonstrate it on
several robotic platforms and in several actual interaction scenarios. It also proved
to be an effective framework for novel contributions about human-robot joint
action \cite{fiore2016planning,devin2016implemented,milliez2016using}, as well as for multi-disciplinary studies \cite{dautenhahn2006may,koay2007exploratory,Ros2010b,dehais2011physiological,ferreira2015users,GharbiROMAN2015} .

@@

\paragraph{Perspective Taking} \emph{Visual} perspective taking refers to the
ability for visually perceiving the environment from another person's point of view.
This ability allows us to identify the objects in situations where the visual
perception of one person differs from the other one. In developmental
psychology, one typical example consists of two similar objects in a room (\eg
two balls) where both are visible for the child, but only one is visible for
the adult. Thus, when the adult asks the child to hand over ``the ball'', the
child is able to correctly identify which ball the adult is referring to (\ie
the one visible from the adult point of view), without asking~\cite{Moll2006}. This ia typically an ability our robot has thanks to the proposed architecture.

@@

\begin{itemize}
\item \emph{Reachable} enables the robot to estimate the agent's ability to
    reach for an object, which is instrumental for effective social task
    planning. For example, if the human asks the robot to give her/him an object,
    the robot must compute a transfer point where she/he s able to get the
    object afterwards.  Reachability is computed for each agent (human or robot) based on
    Generalised Inverse Kinematics and collision detection.

>>>>

We focus on a specific class of interactions: human-robot collaborative task
achievement~\cite{alami2013human} 
supported by multi-modal and situated communication. Figure~\ref{fig:hri-dec}
illustrates this context: the human and the robot share a common space and exchange
information through multiple modalities (we specifically consider verbal
communication, deictic gestures and social gaze), and the robot is expected to achieve
interactive object manipulation, fetch and carry tasks and other similar
chores by taking into account, at every stage, the intentions, beliefs,
perspectives, skills of its human partner.  Namely, the robot must be able to
recognise, understand and participate in communication situations, both explicit
(\eg the human addresses verbally the robot) and implicit (\eg the human points
to an object); the robot must be able to take part in joint actions, both
pro-actively (by planning and proposing resulting plans to the human) and
reactively; the robot must be able to move and act in a safe, efficient and
legible way, taking into account social rules like proxemics.

@@

This translates into several decisional, planning, representation skills that
need to be available to the robot~\cite{alami2011robot}. It must be able \item
to represent and manipulate symbolic belief states, \item to acquire and keep
them up-to-date with respect to the state of the world and the task at hand,
\item to build and iteratively refine shared (human-robot) plans, \item to
instantiate and execute the actions it has to perform, and conversely, to
monitor those achieved by its human partner.

@@

Importantly, this architecture is fully implemented and we demonstrate it on
several robotic platforms and in several actual interaction scenarios. It also proved
to be an effective framework for novel contributions about human-robot joint
action~\cite{fiore2016planning,devin2016implemented,milliez2016using}, as well
as for multi-disciplinary studies~\cite{dautenhahn2006may,koay2007exploratory,Ros2010b,dehais2011physiological,ferreira2015users,GharbiROMAN2015}.

@@

\paragraph{Perspective Taking} \emph{Visual} perspective taking refers to the
ability for visually perceiving the environment from another person's point of view.
This ability allows us to identify the objects in situations where the visual
perception of one person differs from the other one. In developmental
psychology, one typical example consists of two similar objects in a room (\eg
two balls) where both are visible for the child, but only one is visible for
the adult. Thus, when the adult asks the child to hand over ``the ball'', the
child is able to correctly identify which ball the adult is referring to (\ie
the one visible from the adult point of view), without asking~\cite{Moll2006}.
Our architecture endows the robot with such a cognitive skill.

@@

\begin{itemize}
\item \emph{Reachable} enables the robot to estimate the agent's ability to
    reach for an object, which is instrumental for effective social task
    planning. For example, if the human asks the robot to give her an object,
    the robot must compute a transfer point where she is able to get the
    object afterwards.  Reachability is computed for each agent (human or robot) based on
    Generalised Inverse Kinematics and collision detection. More than that, our robot is able 
    to compute an estimate of the effort the
